---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox) 
#devtools::install_github("rstudio-education/dsbox")
```

This never works. 
```{r}
githubURL_1 <- "https://github.com/DataScience4Psych/DataScience4Psych/raw/main/data/raw-data/laquinta.rda"

githubURL_2 <- "https://github.com/DataScience4Psych/DataScience4Psych/raw/main/data/raw-data/dennys.rda"

load(url(githubURL_1))
load(url(githubURL_2))

```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
```

### Exercise 1

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 2

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 3

...

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...

Add exercise headings as needed.

